\section{Background}
\begin{comment}
Build up the context that the reader could read, like a story, to understand more about the problem you’re addressing, the phenomena you are talking about. If the paper is about an internet ban in Bangladesh, tell the story about how the ban was put in place, what was the timeline like, who said what in popular press, and so on. If the research was conducted in the context of an organization of health/outreach workers, talk about the organization, its charter, what it has done/is doing.
\end{comment}
\begin{comment}
With its massive population of over a billion people, India is faced with the logistical challenge of dispensing quality health care to each and every citizen irrespective of geographical location and economic status. Today, even in the capital city of Delhi, there is a vast difference in the level of access and quality of health care received by people from different socio-economic groups.

The Delhi government has proposed an interesting way to tackle this. It is planning to set up a 3-tier system where the lowest tier is a system of ‘Mohalla Clinics’, government clinics in each neighborhood which provide free consultation, tests and medicines. While the existing dispensaries are meant to cater to 50,000 people, each clinic will cater to around 10,000 people in a locality. So far around a hundred clinics have been set up and the government aims to open 1000 such clinics by the end of the year.

According to one doctor I met, the clinics have been set up haphazardly by the government as an immediate response to the crisis. Mohalla clinics are being set up in rented rooms or with pre-made structures around the city. Those running them are doctors coming out of retirement or wanting to give back to society. The government pays the doctors around Rs 30 for every patient they see which is lower than what they would have received at a private practice. The clinics in operation have little in common save the promise to provide quality health care, the facilities available and the staff employed vary.

The two clinics in my area were open only from 9am to 1pm, 6 days a week, during the time many people work. One clinic I visited had a waiting time of around 2 hours while the other had practically no waiting time, though both saw the same number of visitors in a day. At the moment, the clinics are relying on word of mouth to bring new customers. 
*****
\end{comment}
\textcolor{red}{ [
health scenario in Delhi
current system
proposed system by govt
current implementation of proposed system
questions revolving around the proposed system]
}

Despite advances made in public policy and infrastructure in health care in Delhi, results have been mixed. While having the lowest death rates and one of the best life expectancy levels in the country, infant mortality is high and there is a significant gap in the uptake of maternal and child care among slum and non-slum populations. Given the significantly better availability of health facilities as compared to other cities, (opposite of universal coverage?) in areas such as institutional deliveries suggests the persistence of socioeconomic inequalities in access \cite{mazumdar2015health}.

To cover the last mile in health care, the Delhi government has proposed a three tier system that supports the existing network of government hospitals and dispensaries that offer free health care. \cite{article}. At the lowest tier of the proposed system are neighborhood clinics or Mohalla clinics that are operated by one doctor assisted by staff and offer free consultations, medication and over 200 tests. At the secondary level, polyclinics will be set up that provide specialized services. Existing large government hospitals make up the top-most level of this system.

%To [high level aim of the initiative, cite here, press release?], the Delhi government has proposed a 3-tier system that supports the existing network of government hospitals and dispensaries that offer free health care. The goal is \cite{}.

%At the lowest level of this system are neighborhood clinics or 'Mohalla clinics', each of which cater to 10,000 people living in that locality. Each of these clinics is manned by one doctor and provides free consulting, free medicines and tests. These clinics operate from 9am to 1pm, six days a week.

%The next tier of the proposed system involves polyclinics that offer specialized services.

%As of August 2016, there are 108[check] Mohalla clinics and 2[check] polyclinics set up by the government. Our study will be focusing on two Mohalla clinics. 