\section{Discussion}

\textcolor{red}{[To be completed]}

* discuss our classification further - while we have used this classification - Perspective of people who are coming, not coming, doctors - cannot say that they are not coming, cannot conclusively cannot say that middle income are coming. There’s a gap - how can you close the gap further - how to make it more effective?

* Improve design of the Mohalla clinics (includes timings and location) to make it more accessible- make design recommendations - improving function of dispensaries over building more clinics?

* awareness of the clinics - announcement systems for immunization etc - leverage such informal systems here?

* Scope for ICTD - supplement network of hospitals, health care providers, patients - current use of tech very limited, design recommendations - info dissemination - support systems

* Are design objectives met? collecting data that is "useful" and provide a feedback system to improve functioning and design of the clinics

* category - discouraging use by non-target - is it ethical to actively do that? perhaps focusing on where there is a need vs actively discouraging others

* offer a lens to view an intervention's success in the context of its use by target AND non-target populations. (Maybe this should go in conclusion) - discuss who this is meant to be applicable too - desired readers?

%Class + socio-economic: look at references for class

%Designing services and challenges involved, how to ensure services are adopted?

%Design recommendations -
%Waiting time - ICTD paper 
%Info factor, how it is provided eg morning, location
%Sustainability of the intervention

%Factors leading to what is overlooked and say stuff was overlooked
%Extending the service to other 

%Is there a motivation for them to go to a clinic 

%Other aspect: how do you share info about the intervention - info gap, social gap
%Incentives to stay engaged