\documentclass{sigchi}
\pagenumbering{arabic}


% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

\makeatletter
\def\url@leostyle{
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={Designing for Use and Non-Use: A Perspective from Neighborhood Clinics},
pdfauthor={Azra Ismail},
% * <aismail1997@gmail.com> 2016-09-13T12:25:10.966Z:
%
% ^.
pdfkeywords={SIGCHI, proceedings},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

\newcommand\tabhead[1]{\small\textbf{#1}}

\begin{document}

%change this!!! - not sure what we mean
\title{Designing for Use and Non-Use: A Perspective from Neighborhood Clinics}
\numberofauthors{3}
\author{
  \alignauthor 1st Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{Address}\\
    \email{e-mail address}\\
    \affaddr{Optional phone number}
  \alignauthor 2nd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{Address}\\
    \email{e-mail address}\\
    \affaddr{Optional phone number}    
  \alignauthor 3rd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{Address}\\
    \email{e-mail address}\\
    \affaddr{Optional phone number}
}

\maketitle
\begin{abstract}
%[We present a study/examination/analysis of - We do X to understand Y. We highlight X, discussing Y, and conclude with Z. 
%1. What this paper is about
%2. Motivation
%3. Approach
%4. Findings
%5. Broader applicability
%6. Paper takeaways
%}
We present a qualitative study of Mohalla (neighborhood) Clinics - an intervention introduced by the state government of Delhi (India) in 2015 to provide basic health care services to the underprivileged. Though these clinics were introduced with the explicit objective of targeting the ``weakest sections of society'', actual use of these clinics tells a different story. We conducted a two-month field study focused on two Mohalla Clinics and their use by local residents belonging to various socioeconomic groups. Our findings highlight the factors affecting use of the clinics by targeted underprivileged sections of society when the same services are also desired (and availed) by the non-target population. We draw on our findings to inform the design of health interventions towards use and non-use by identified target groups. More broadly, we provide insights for researchers and practitioners designing interventions for global development, targeting underserved individuals and communities.

% present a perspective on the design of HCI4D interventions through the lens of design factors (encouraging vs mediate) use and non-use by target and non-target groups by presenting the case of Mohalla (or neighborhood) clinics introduced in Delhi. [Motivation?] We highlight the need to focus on designing for use and non-use as much as usability by presenting our findings from a multi-site ethnographic study on the use of the health care system [local state-supported]. Our study of the Mohalla clinics demonstrates the role [unpack what influences use/non-use] of socioeconomic, geographic and gender-related factors in the process of choosing to use a health care facility and we argue that we can design for use by the target group by taking these factors into consideration. Thus, we extend the definition of use to include processes that occur outside direct interaction with the technology. We invite the HCI4D community and policy makers to design their interventions for use by their target group.
\end{abstract}

\keywords{Public health; India; use; non-use; HCI4D}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} 

\input{introduction.tex}
\input{relatedwork.tex}
\input{methodology.tex}
\input{findings.tex}
\input{discussion.tex}

\section{Conclusion}
\textcolor{red}{[To be completed]}
%more here? 
The limited reach of the Mohalla clinics to its target group makes a case for viewing an intervention through the lens of designing for use and non-use by the target and non-target groups to ensure that it reaches those in 'need' of the intervention. While designing for use, the interplay of factors affecting use such as the design of the intervention, socioeconomic status, care by the actors and cultural norms should be taken into account. We offer this approach of 'designing for use and non-use' to the larger HCI4D community, as well as policy makers and organizations designing interventions.
\balance

\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{references}

\end{document}
